Inferring the Recombinant Genealogy of a Pandemic Pathogen in Real Time

### 2025-09-10 latex/main.tex
fix deletions

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{pango_x_subgraphs}
\caption{
Illustrative subgraphs in the ARG.
(A) Subgraph around the recombination event associated with the XA.
The "Group A" sequences identified by Jackson et al.\cite{Jackson2021}) are attached to this event.
(B) Subgraph around the recombination event associated with a group of ``nested'' Pango Xs; and
(C) Subgraph around the MRCA of the closely related non-recombinants XN and XAU.
For more detailed visualizations of these subgraphs, see Document S2.
}
\label{fig:subgraphs}
\end{figure}

@@

\begin{table}
\centering
\caption{Most commonly observed deletions in the ARG or Li et al. (2023).} 
\label{tab:common_dels}
\begin{tabular}{rrcrrrr}
\toprule
\multicolumn{3}{c}{} & \multicolumn{2}{c}{Sc2ts ARG} & \multicolumn{2}{c}{Li et al. (2023)} \\
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
Start & Length & Region & Count & Frequency (\%) & Count & Frequency (\%)\\
\midrule
28271 & 1 & non-coding & 1422469 & 57.3078 & 3853692 & 42.1183 \\
28248 & 6 & ORF8 & 1114712 & 44.9090 & 3026186 & 33.0742 \\
22029 & 6 & S / S1-NTD & 1114415 & 44.8970 & 3010665 & 32.9046 \\
11288 & 4 & ORF1ab / NSP6 & 871838 & 35.1242 & N/A & N/A \\
28362 & 9 & N & 871778 & 35.1218 & 3939164 & 43.0525 \\
21765 & 6 & S / S1-NTD & 825628 & 33.2625 & 3179887 & 34.7541 \\
21633 & 9 & S / S1-NTD & 532084 & 21.4364 & 1941962 & 21.2244 \\
11292 & 5 & ORF1ab / NSP6 & 531943 & 21.4307 & N/A & N/A \\
6513 & 3 & ORF1ab / NSP3 & 341714 & 13.7668 & 1984683 & 21.6913 \\
11283 & 5 & ORF1ab / NSP6 & 339935 & 13.6951 & 8360 & 0.0914 \\
21988 & 8 & S / S1-NTD & 339770 & 13.6885 & 590 & 0.0064 \\
22194 & 3 & S / S1-NTD & 313878 & 12.6454 & 1833050 & 20.0340 \\
11288 & 9 & ORF1ab / NSP6 & 311566 & 12.5522 & 3040576 & 33.2315 \\
21991 & 3 & S / S1-NTD & 308800 & 12.4408 & 912944 & 9.9779 \\
29762 & 1 & non-coding & 38030 & 1.5321 & N/A & N/A \\
29781 & 1 & non-coding & 36112 & 1.4549 & N/A & N/A \\
29769 & 1 & non-coding & 34315 & 1.3825 & N/A & N/A \\
29774 & 1 & non-coding & 33503 & 1.3498 & N/A & N/A \\
29779 & 1 & non-coding & 30515 & 1.2294 & N/A & N/A \\
11283 & 9 & ORF1ab / NSP6 & 60 & 0.0024 & 2011934 & 21.9891 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{pango_x_subgraphs}
\caption{
Illustrative subgraphs in the ARG.
(A) Subgraph around the recombination node associated with the XA.
Two "Group A" recombinant samples reported by Jackson et al.\cite{Jackson2021}) are shown.
(B) Subgraph around the recombination node associated with a group of ``nested'' Pango X lineages; and
(C) Subgraph around the MRCA of the closely related non-recombinants XN and XAU.
The nodes assigned to a Pango X lineage are colored by that lineage.
The numbers inside the colored boxes indicate
the number of samples assigned to the Pango X lineage indicated by the same color.
The numbers below the vertical dashed lines indicate
the total number of samples within a collapsed clade.
For each recombination node, a genome schematic shows
the location of its inferred breakpoint interval relative to the Spike gene.
The ancestry above the parents of the recombination nodes or the MRCA is not shown for clarity.
For more detailed visualizations of these subgraphs, see Document S2.
}
\label{fig:subgraphs}
\end{figure}

@@

\begin{table}
\centering
\caption{Most commonly observed deletions in the ARG or Li et al. (2023).} 
\label{tab:common_dels}
\begin{tabular}{rrcrrrr}
\toprule
\multicolumn{3}{c}{} & \multicolumn{2}{c}{Sc2ts ARG} & \multicolumn{2}{c}{Li et al. (2023)} \\
\cmidrule(lr){4-5} \cmidrule(lr){6-7}
Start & Length & Region & Count & Frequency (\%) & Count & Frequency (\%) \\
\midrule
28271 & 1 & non-coding & 1422469 & 57.3078 & 3853692 & 42.1183 \\
28248 & 6 & ORF8 & 1114712 & 44.9090 & 3026186 & 33.0742 \\
22029 & 6 & S / S1-NTD & 1114415 & 44.8970 & 3010665 & 32.9046 \\
11288 & 4 & ORF1ab / NSP6 & 871838 & 35.1242 & N/A & N/A \\
28362 & 9 & N & 871778 & 35.1218 & 3939164 & 43.0525 \\
21765 & 6 & S / S1-NTD & 825628 & 33.2625 & 3179887 & 34.7541 \\
21633 & 9 & S / S1-NTD & 532084 & 21.4364 & 1941962 & 21.2244 \\
11292 & 5 & ORF1ab / NSP6 & 531943 & 21.4307 & N/A & N/A \\
6513 & 3 & ORF1ab / NSP3 & 341714 & 13.7668 & 1984683 & 21.6913 \\
11283 & 5 & ORF1ab / NSP6 & 339935 & 13.6951 & 8360 & 0.0914 \\
21988 & 8 & S / S1-NTD & 339770 & 13.6885 & 590 & 0.0064 \\
22194 & 3 & S / S1-NTD & 313878 & 12.6454 & 1833050 & 20.0340 \\
11288 & 9 & ORF1ab / NSP6 & 311566 & 12.5522 & 3040576 & 33.2315 \\
21991 & 3 & S / S1-NTD & 308800 & 12.4408 & 912944 & 9.9779 \\
29762 & 1 & non-coding & 38030 & 1.5321 & N/A & N/A \\
29781 & 1 & non-coding & 36112 & 1.4549 & N/A & N/A \\
29769 & 1 & non-coding & 34315 & 1.3825 & N/A & N/A \\
29774 & 1 & non-coding & 33503 & 1.3498 & N/A & N/A \\
29779 & 1 & non-coding & 30515 & 1.2294 & N/A & N/A \\
11283 & 9 & ORF1ab / NSP6 & 60 & 0.0024 & 2011934 & 21.9891 \\
686 & 9 & ORF1ab / NSP1 & N/A & N/A & 115450 & 1.2618 \\
21987 & 9 & S / S1-NTD & N/A & N/A & 1918094 & 20.9635 \\
\bottomrule
\end{tabular}
\end{table}
